% File:     burkelibbey_resume.tex
% Author:   Burke Libbey <burke@burkelibbey.org>
% Modified: <2008-12-08 13:48:47 CST>

\documentclass[margin,line,letterpaper]{resume}

\begin{document}
\name{\Large D. Burke Libbey}
\begin{resume}

  %______________________________________________________________________________________
  % Contact Information
  \section{\mysidestyle Contact\\Information}\vspace{2mm}

  \begin{tabular}{@{} l @{\hspace{76mm}} r}
  181 Campbell Street    & 1.204.232.1160         \\
  Winnipeg, MB~ R3N 1B4  & burke@burkelibbey.org  \\
                         & http://burkelibbey.org \\
  \end{tabular}

  %______________________________________________________________________________________
  % Technical Expertise
  \section{\mysidestyle Technical\\Expertise}

  Proficient with Windows, Mac, and Linux environments. \\
  Fluent in Ruby, JavaScript, \LaTeX , English, PHP, SQL, X/HTML, and CSS.\\
  Conversant in C, MATLAB, Java, Python, Clojure, and others.

  %______________________________________________________________________________________
  % Education
  \section{\mysidestyle Education}

  {\bf B.Sc. Computer Engineering} \vspace{2mm}\\\vspace{1mm}%
  {\sl University of Manitoba} \hfill {\bf Ongoing}

  %______________________________________________________________________________________
  % Employment
  \section{\mysidestyle Work}

  {\bf Chromium 53 Consulting}, Winnipeg, MB \vspace{2mm}\\\vspace{1mm}%
  {\sl Partner} \hfill {\bf August 2008 -- Present}\\
  Started and operated a business specializing in software development, design, and
  consulting for the World Wide Web; Administered several development and production web servers,
  hosting dozens of client domains; Collaborated with partner, contractors, and clients to create
  visually appealing, standards-compliant, and highly dynamic web applications tailored specifically
  to each client's needs.

  {\bf TRLabs}, Winnipeg, MB \vspace{2mm}\\\vspace{1mm}%
  {\sl Researcher, Assistant System Administrator} \hfill {\bf April 2008 -- Present}\\
  Conducted a technical feasibility study on the implementation of a large-scale Wi-Fi
  network to encompass a significant portion of Winnipeg, and compiled the results into a report
  for delivery to the client; Installed and configured Microsoft Exchange to replace the
  existing mail infrastructure across each of the five TRLabs locations in Western Canada;
  Developed a contact and event management system using the Ruby on Rails framework.

  {\bf University of Manitoba Learning Technologies Centre} \vspace{2mm}\\\vspace{1mm}%
  {\sl Digital Resource Developer} \hfill {\bf June 2007 -- September 2008}\\
  Implemented the Ruby on Rails framework to construct an open-source
  community extension to an existsing online peer-reviewed journal system; contributed to the
  University of Manitoba's Virtual Learning Commons;

  {\bf Self} \vspace{2mm}\\\vspace{1mm}%
  {\sl Freelance Web Developer} \hfill {\bf 2006 -- 2008}\\
  Worked closely with clients to develop fully standards-compliant designs; implemented
  an industry-leading CMS to create functional, maintainable systems.

  {\bf It's Time/Web Designs}, Neepawa, MB \vspace{2mm}\\\vspace{1mm}%
  {\sl PHP Programmer} \hfill {\bf 2006}\\
  Made extensive use of PHP in several projects; implemented a PHP/MySQL shopping cart
  system on top of existing site software.

  {\bf Hamel Computer Sales and Service}, Minnedosa, MB \vspace{2mm}\\\vspace{1mm}%
  {\sl Webmaster} \hfill {\bf 2004 -- 2006}\\
  Developed and maintained websites for 20+ clients and managed several internal projects.
  Constructed a complete eCommerce system from the ground up using PHP/MySQL.

  \newpage
  %______________________________________________________________________________________
  % Service
  \section{\mysidestyle Service}

  \begin{list2}
    \item Director of Electronic Communications, U of M Engineering Society, 2007 -- Present
    \item Secretary, U of M IEEE Student Branch, 2007 -- Present
    \item Computer Manager, U of M IEEE Student Branch, 2007 -- 2008
    \item Karate Instructor, Minnedosa Karate Club, 2001 -- 2004
    \item Web Developer, Minnedosa Chamber of Commerce, 2004
  \end{list2}

  %______________________________________________________________________________________
  % Projects
  \section{\mysidestyle Projects}

  \begin{list2}
    \item UM IEEE High Performance Cluster (http://hpc.umieee.com)
    \item UMES Textbook Exchange (http://text.umes.mb.ca)
  \end{list2}


  %______________________________________________________________________________________
  % Awards and Accomplishments
  \section{\mysidestyle Awards and\\Accomplishments}

  \begin{list2}
    \item 1st in Manitoba, ACM International Collegiate Programming Contest Regionals, 2007.
    \item 3rd Kyu, Shotokan Karate (Brown Belt).
    \item Various karate tournament awards in kata, kumite, and team kumite events.
    \item Medallion for Academics throughout high school (2003 -- 2006).
  \end{list2}

  %______________________________________________________________________________________
  % References
  \section{\mysidestyle References}

  {\sl Available on request.}

%________________________________________________________________________________________
\end{resume}
\end{document}

%________________________________________________________________________________________
% EOF

